Apples and Oranges in Adolescent Depression Treatments.

### 2024-01-03 apples_and_oranges.qmd
with various new additions for Charlotte

---
title: Apples and Oranges in Adolescent Depression Treatments.
subtitle: A conceptual and quantiative re-appraisal of control arms in clinical trials.
author:
  - name: Argyris Stringaris
    email: a.stringaris@ucl.ac.uk
    affiliations: 
        - id: ucl_1
          name: University College London
          department: Divisions of Psychiatry and Psychology and Language Science
          address: 1-19 Torrington Place
          city: London, UK
          state: 
          postal-code: WC1E 7HB
          country: United Kingdom
    attributes:
        corresponding: true
    note: 
  - name: Charlotte Burman
    email: c.burman@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Dayna Bhudia
    email: d.bhudia@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Carmen Moreno
    email: cmoreno@hggm.es
    affiliations:
        - id: HGM
          name: Hospital Gregorio Marañón
          department: Department of Psychiatry
          address: 46 C. del Dr. Esquerdo
          city: Madrid
          state:
          postal-code: 28007
          country: Spain
  - name: Samuele Cortese
    email: samuele.cortese@soton.ac.uk
    affiliations:
        - id: soton
          name: University of Southampton
          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
          address: Highfield Campus, Building 44
          city: Southampton
          state:
          postal-code: SO17 1BJ
          country: United Kingdom
  - name: Georgina Krebs
    email: g.krebs@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note: 
abstract: |
  To follow
keywords: 
  - depression
  - adolescents
  - antidepressants
  - psychotherapy
date: last-modified
bibliography: emotion_concepts_paper.bib
format: 
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
---

@@

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
library(tidyverse)
df_long_for_metan <- read.csv("~/apples_and_oranges/df_long_for_metan")

@@

@@

In order to conduct a met

>>>>

---
title: Apples and Oranges in Adolescent Depression Treatments.
subtitle: A conceptual and quantiative re-appraisal of control arms in clinical trials.
author:
  - name: Argyris Stringaris
    email: a.stringaris@ucl.ac.uk
    affiliations: 
        - id: ucl_1
          name: University College London
          department: Divisions of Psychiatry and Psychology and Language Science
          address: 1-19 Torrington Place
          city: London, UK
          state: 
          postal-code: WC1E 7HB
          country: United Kingdom
    attributes:
        corresponding: true
    note: 
  - name: Charlotte Burman
    email: c.burman@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Dayna Bhudia
    email: d.bhudia@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Carmen Moreno
    email: cmoreno@hggm.es
    affiliations:
        - id: HGM
          name: Hospital Gregorio Marañón
          department: Department of Psychiatry
          address: 46 C. del Dr. Esquerdo
          city: Madrid
          state:
          postal-code: 28007
          country: Spain
  - name: Samuele Cortese
    email: samuele.cortese@soton.ac.uk
    affiliations:
        - id: soton
          name: University of Southampton
          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
          address: Highfield Campus, Building 44
          city: Southampton
          state:
          postal-code: SO17 1BJ
          country: United Kingdom
  - name: Georgina Krebs
    email: g.krebs@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note: 
abstract: |
  To follow
keywords: 
  - depression
  - adolescents
  - antidepressants
  - psychotherapy
date: last-modified
bibliography: emotion_concepts_paper.bib
format: 
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super

---

@@

# Method
## Studies included

NOTE: **Charlotte** to please check code lines 986 to 1121
NOTE: **Charlotte** please check that the studies I have in the *df_long_for_metan* dataframe makes sense and correspond to what you would expect. In the beginning of the results below, I explain in detail what is missing where.

## Statistical Analysis
### Measures of Effect
As the measure of effect of each individual study, we used the Standardised Mean Difference (SMD), which we defined following NOTE: **Charlotte** cite Lakens 2013 and in there Cummings 2012, as:

$$\frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$  {#eq-3}

where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the study respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations. NOTE **Charlotte**, please add note here with what we did to impute SDs where missing, e.g. using the pre to impute the post etc. In general state here the rules we used citing the Cochrane book.

For the purposes of metanalysis, it is necessary to estimate a standard error of the change score, that is of the SMD. This is calculated according to:

$$ \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$          {#eq-4}

where $n$ refers to the study sample size and $r_{t_{1}t_{2}}$ refers to the correlation between the outcome score obtained at baseline and at the end point. This correlation is typically not reported in studies and is often imputed using previously reported correlations for the instruments used. However, this practice has given rise to concerns about misestimation. Whilst such misestimation is possible, there is no reason to expect that it would be systematic, i.e. bias estimation of the effects for the control group of medication compared to those of psychotherapy. Still, to alleviate such concerns we have used a simulations.

In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics:

$$SE_{change} \sim \mathcal{TN}(\mu, \sigma, a, b)
$$ {#eq-5}

for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively. We then used these simulated datasets in the subsequent metanalyses.

```{r, warning=FALSE, message = FALSE, echo=FALSE}
library(tidyverse)
# Start here------------------------------------------------------
# import master dataset

df_appl_v_orange <-readxl:: read_excel("df_appl_v_orange.xlsx")

#Need to use SMDs, ie our Cohen's d and then use Standard error of SMD, to achieve this
# I need reliabilities.

# note re: CDRS reliability from here https://www.liebertpub.com/doi/epdf/10.1089/104454601317261546 
# Using a   2-week interval, and different psychiatrists from the first to the second assessment, 
# Poz-nanski et    al. (1984) demonstrated high reliability (r=   0.86) 
# for the CDRS-R total score in 53 clinic-referred6- to 12-year-olds.

### A few more tidying things from Argyris before doing metanalyses
# # discovered an error in the percentage women o fthe Fristad study. I have checked in the
# # cuijpers dataset and the correct percentage is 43.1, but could not verify with the paper as it is not in 
# # our folder and after a quick search I could not find it online either. Messaged Charlotte on Discord to
# # check again.
df_appl_v_orange[df_appl_v_orange$study_ID=="Fristad, 2019_cbt + placebo_placebo",]$percent_women <-43.1

# Create SEs proportions for percentage women --------------------------------------------

# # We also need to calculate SE for proportion women for the baseline calculations
# # for proportions, this is calculated as sqrt(p(1-p)/n), which I implement stepwise below

product_perc_women <-  (df_appl_v_orange$percent_women/100)*
  (1-(df_appl_v_orange$percent_women/100) )

total_n <- df_appl_v_orange$baseline_n_active + 
  df_appl_v_orange$baseline_n_control

df_appl_v_orange$percent_women_std_error <- sqrt(product_perc_women/total_n )

# Calculate SE for baseline severity --------------------------------------

df_appl_v_orange$baseline_st_error_active <- 
  df_appl_v_orange$baseline_sd_active/sqrt(df_appl_v_orange$baseline_n_active)

df_appl_v_orange$baseline_st_error_control <-
  df_appl_v_orange$baseline_sd_control/sqrt(df_appl_v_orange$baseline_n_control)

# Turn into a long database with unique rows ------------------------------

### Important: create a dataset that will have unique control studies (see problem that we identified with Charlotte, 
#namely common control conditions)
# create new id with Charlotte to help with better identification and work with duplicates (see below) 
df_appl_v_orange  <- df_appl_v_orange  %>%
  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
                                  .default = study ))

# Step 1: keep only the rows with the top instrument in our hierarchy
df_with_distinct_instruments <-  df_appl_v_orange %>%          
  group_by(new_study_id) %>% 
  filter(instrument_value == min(instrument_value)) # coded for the smallest number to be best.

# Step 2: turn dataframes to long
# A: turn long the rows with active
turn_long_active_type <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, active_type, psy_or_med, baseline_n_active, cohens_d_active) %>% 
  pivot_longer(cols = c(cohens_d_active), 
               names_to = "arm_effect_size", 
               values_to = "cohens_d")

# also rename active_type to treatment for the merge below.
turn_long_active_type <- rename(turn_long_active_type,treatment = active_type,
                                baseline_n = baseline_n_active)

# # to illustrate the issue, here we have one study with two controls for which the active at the moment, also exists twice. 
# turn_long_active_type[turn_long_active_type$new_study_id == "Stallard, 2012",]
# # but here another one where the same study reasonably contributes two actives, fluoxetine and duloxetine.
# turn_long_active_type[turn_long_active_type$new_study_id == "Atkinson, 2014",]

# we now need to go through each study id and remove duplicates
turn_long_active_type <-
  turn_long_active_type %>% 
  group_by(new_study_id) %>% 
  distinct(treatment, .keep_all = TRUE)

# # Now checking if this worked with the studies that I used to illustrate the problem above. 
# turn_long_active_type[turn_long_active_type$new_study_id == "Stallard, 2012",]
# turn_long_active_type[turn_long_active_type$new_study_id == "Atkinson, 2014",]
# # also check one which is single to make sure it is kept
# turn_long_active_type[turn_long_active_type$new_study_id == "Ackerson, 1998",]

# B: turn long control rows
turn_long_control_type <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, control_type, psy_or_med, baseline_n_control, cohens_d_control) %>% 
  pivot_longer(cols = c(cohens_d_control), 
               names_to = "arm_effect_size", 
               values_to = "cohens_d")

# also rename active_type to treatment for the merge below.
turn_long_control_type <- rename(turn_long_control_type,treatment = control_type,
                                 baseline_n = baseline_n_control)

# # to illustrate the issue, here we have one study with two controls that are reasonable. 
# turn_long_control_type[turn_long_control_type$new_study_id == "Stallard, 2012",]
# # but here another one where the same study reasonably contributes two placebos
# turn_long_control_type[turn_long_control_type$new_study_id == "Atkinson, 2014",]

# we now need to go through each study id and remove duplicates
turn_long_control_type <-
  turn_long_control_type %>% 
  group_by(new_study_id) %>% 
  distinct(treatment, .keep_all = TRUE)

# # Now checking if this worked with the studies that I used to illustrate the problem above. 
# turn_long_control_type[turn_long_control_type$new_study_id == "Stallard, 2012",]
# turn_long_control_type[turn_long_control_type$new_study_id == "Atkinson, 2014",]
# # also check one which is single to make sure it is kept
# turn_long_control_type[turn_long_control_type$new_study_id == "Ackerson, 1998",]

### Now merge the active and control datasets
df_long_for_metan <-rbind(turn_long_active_type, turn_long_control_type)
#dim(df_long_for_metan ) #check dimension
#make sure no study lost
#length(unique(df_long_for_metan$new_study_id ) ) == # #length(unique(df_appl_v_orange$new_study_id ) )

# Now check again the studies with muliple arms
# Now checking if this worked with the studies that I used to illustrate the problem above. 
# df_long_for_metan[df_long_for_metan$new_study_id == "Stallard, 2012",]
# df_long_for_metan[df_long_for_metan$new_study_id == "Atkinson, 2014",]
# # also check one which is single to make sure it is kept
# df_long_for_metan[df_long_for_metan$new_study_id == "Ackerson, 1998",]

# save this as the master dataframe  --------------------------------------
# use this datafram to perform all operations below in quarto
# ask Charlotte to check steps above (lines 986 to 1121)
write.csv(df_long_for_metan, "df_long_for_metan", row.names = F)

########### simulate so that each study has a value from a distribution of 
######## of correlations.

# I will generate random numbers per study id from a distribution with these parameters. 
# it is reasonable to generate one random correlation value per study as there is no reason why the correlation should
# systematically vary within studies

# I have created a function for this
library(tidyverse)
library(truncnorm)

df_long_for_metan <- read.csv("~/apples_and_oranges/df_long_for_metan")

simulate_dataframes_for_st_errors <- function(df, num_repetitions, seed, n, a, b, mean, sd) { # n refers to the number
                                                                                              # of unique ids to which a correlation coef
                                                                                              # is allocated.
  set.seed(seed)

  # Empty list to store simulated dfs
  list_df_simulated <- list()

  for (i in 1:num_repetitions) {
    # Simulate the vector
    simulated_correlations_vector <- truncnorm::rtruncnorm(n, a, b, mean, sd)  #using the truncnorm to create correlations

    # Create a copy of the original dataframe
    df_simulated_copy <- df

    # Add/update the sims column
    df_simulated_copy$correlation_sim_values <- simulated_correlations_vector[match(df_simulated_copy$new_study_id, unique(df_simulated_copy$new_study_id))]

    # Remove duplicated columns
    df_simulated_copy <- df_simulated_copy[, !duplicated(colnames(df_simulated_copy))]

    # Calculate the ses
    df_simulated_copy <- df_simulated_copy %>% 
      group_by(new_study_id, baseline_n) %>% 
      mutate(simulated_se = sqrt(((2*(1-correlation_sim_values))/baseline_n) + 
                                   (cohens_d^2/(2*baseline_n))))

    # Add the simulated dataframe to the list
    list_df_simulated[[i]] <- df_simulated_copy
  }

  return(list_df_simulated)
}

list_df_simulated <-  simulate_dataframes_for_st_errors (df = df_long_for_metan, 
                                              num_repetitions = 1000, 
                                              seed  = 1974,
                                              n = length(unique(df_long_for_metan$new_study_id)), 
                                              a = 0.45, 
                                              b = .9, 
                                              mean = 0.65, 
                                              sd = 0.2)

#check this worked

#list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_se")] # looks right
#summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave

### Random Effects Metaregression
We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package. The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
Therefore, we can estimate a two stage model with:

$$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
$$ {#eq-5}

$$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
$$ {#eq-6}

where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$. Whereas $\theta_i$ is a study-specific instantiation of the distribution of effect sizes, with $\tau^2$ representing heterogeneity.

This then gives rise to:

$$Y_i = x_i\beta_i + u_i + \epsilon_i$$ {#eq-7}

where,

$$u_i \sim N(0, \tau^2) $${#eq-8}

which describes the deviation of each study from the mean of the distribution, and,

$$\epsilon_i \sim N(0, \sigma^2)$$ {#eq-9}

We can then specify the following model to obtain the means of each arm of the trials as follows:

$$ \begin{aligned}
    Υ_i &=
    \begin{cases}
        0 & MedControl: b_0 + u_i + \epsilon_i\\
        1 & MedActive:  b_0 + b_{1_{i}} +  u_i + \epsilon_i \\
        2 & PsyActive:  b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\
        3 & PsyControl: b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\
    \end{cases}
\end{aligned}$$  {#eq-10}

where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g. for level 3, $b_{3_{i}}$ the psychotherapy controls. The confidence intervals of the means are constructed in the standard way using the standard errors of the 
Similarly, each coefficient represents the contrast between the reference category and each level, for an exmaple and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms. Inference on the contrasts is done as follows:

$$
z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
$$ {#eq-11}

We used maximum likelihood (REML) to estimate model and applied  Hartung-Knapp adjustment to reduce the chance of false positives (NOTE: **Charlotte**cite Ioannides on this).

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
library(tidyverse)

@@

df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
```

We then applied metaregression to obtain the means and confidence intervals of each of the four arms.

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Run metaregression ------------------------------------------------------
library(metafor)
# add a new multilevel variable for the regression

for(i in 1: length(list_df_simulated)){
  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
    )

  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor

  # relevel so that medication control becomes the reference category for the regression
  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
}

# check it worked
# list_df_simulated[[2]] %>% 
#   dplyr:: select(psy_or_med, arm_effect_size, four_level_var)

# specify the model 
model_1 <- as.formula(~ four_level_var)

# run the metaregression
list_model_1_meta_reg <- list()

for(i in 1: length(list_df_simulated)){

  list_model_1_meta_reg[[i]] <- rma(yi = cohens_d, 
                                    sei = simulated_se, 
                                    data = list_df_simulated[[i]] , 
                                    method = "ML", 
                                    mods = model_1 , 
                                    test = "knha")

}

# list_model_1_meta_reg[[2]]

# Function to extract parameters (coefs, ses, CI) for each level of the dummy variable
# it is an awkward one, because I couldnt' come up with a better way to add the intercept to each coefficient
# given the named output of the built in coef function. 
# here I exctract the coeffcients
extract_coefficients_func <- function(df_with_coefs){
  list_coefs <- list()
  coefs <- 0
  coefficient_output <- 0

  for(i in 1: length(coefficients(df_with_coefs))){

    temp_vec <- c(0, rep(coefficients(df_with_coefs)[[1]], 
                         length(coefficients(df_with_coefs)) - 1 ))
    coefs[i] <- coef(df_with_coefs)[[i]]

    coefficient_output <- temp_vec + coefs

    st_error_output <- df_with_coefs$se

    df_coefficients <- data.frame(cbind(coefficients = coefficient_output, se = st_error_output ))

    df_coefficients$lower_bound <- df_coefficients$coefficients - 1.96*df_coefficients$se
    df_coefficients$upper_bound <- df_coefficients$coefficients + 1.96*df_coefficients$se
  }
  return (df_coefficients )
}

# dummy_var_means <- extract_coefficients_func(list_model_1_meta_reg[[1]])

list_dummy_var_means <-lapply(list_model_1_meta_reg, extract_coefficients_func)

# this is the way to get the means and SEs from the simulation across all datasets.

df_mean_coefs_from_sim <- data.frame(

  condition = levels(list_df_simulated[[1]]$four_level_var),

  mean_coefficient = c(mean(sapply(list_dummy_var_means, function(df) df[1,1])),
                      mean(sapply(list_dummy_var_means, function(df) df[2,1])),
                      mean(sapply(list_dummy_var_means, function(df) df[3,1])),
                      mean(sapply(list_dummy_var_means, function(df) df[4,1]))),

  mean_se = c(mean(sapply(list_dummy_var_means, function(df) df[1,2])),
              mean(sapply(list_dummy_var_means, function(df) df[2,2])),
              mean(sapply(list_dummy_var_means, function(df) df[3,2])),
              mean(sapply(list_dummy_var_means, function(df) df[4,2])))

)

# and add the CIs

df_mean_coefs_from_sim$upper_ci <- df_mean_coefs_from_sim$mean_coefficient + 1.96 * df_mean_coefs_from_sim$mean_se

df_mean_coefs_from_sim$lower_ci <- df_mean_coefs_from_sim$mean_coefficient - 1.96 * df_mean_coefs_from_sim$mean_se
# df_mean_coefs_from_sim # this is now the dataframe containing the means you need for plotting.

#also, add the n of studies non missing from variable created above
#important first create the same condition variable: 
df_count_studies_not_missing$condition <- str_replace_all(df_count_studies_not_missing$condition, "_", " ")

# I needed to join them because of the relevelling, the rows would not align otherwise.
# df_mean_coefs_from_sim <- right_join(df_mean_coefs_from_sim, df_count_studies_not_missing)

# need to merge this with the count studies variable to obtain the ks
library(forcats)
ordering_criterion <- unique(df_mean_coefs_from_sim$condition)

# 
df_count_studies_not_missing <- df_count_studies_not_missing %>% arrange(ordering_criterion) %>%
  mutate(condition = fct_relevel(condition, levels = unique(condition)))
# I will use this for plotting below.

```
We examined the variability that the simulations of the correlations of the pre-post outcomes produced. As shown in Supplemenatry Table 2, the standard deviation of the simulated mean varied in the third decimal point, indicating minimal influence of the correlations on the outcomes.

NOTE: **Charlotte**, this should be moved to the supplement at Table 2
```{r, warning=FALSE, message = FALSE, echo=FALSE}
variability_in_sims <- data.frame (mean_coefficient = c(mean(sapply(list_dummy_var_means, function(df) df[1,1])),
                      mean(sapply(list_dummy_var_means, function(df) df[2,1])),
                      mean(sapply(list_dummy_var_means, function(df) df[3,1])),
                      mean(sapply(list_dummy_var_means, function(df) df[4,1]))),

sd_coefficient = c(sd(sapply(list_dummy_var_means, function(df) df[1,1])),
                      sd(sapply(list_dummy_var_means, function(df) df[2,1])),
                      sd(sapply(list_dummy_var_means, function(df) df[3,1])),
                      sd(sapply(list_dummy_var_means, function(df) df[4,1]))),

  mean_se = c(mean(sapply(list_dummy_var_means, function(df) df[1,2])),
              mean(sapply(list_dummy_var_means, function(df) df[2,2])),
              mean(sapply(list_dummy_var_means, function(df) df[3,2])),
              mean(sapply(list_dummy_var_means, function(df) df[4,2]))),

  sd_se = c(sd(sapply(list_dummy_var_means, function(df) df[1,2])),
              sd(sapply(list_dummy_var_means, function(df) df[2,2])),
              sd(sapply(list_dummy_var_means, function(df) df[3,2])),
              sd(sapply(list_dummy_var_means, function(df) df[4,2])))
)

@@

Table 1 shows the results containing the means and standard errors for each level, derived as the average of 1000 metanalyses. 
```{r, warning=FALSE, message = FALSE, echo=FALSE}
# for some reason doesn't work, but will make work.
# tab_1_df <- df_mean_coefs_from_sim[, 1:length(df_mean_coefs_from_sim)-1]
# knitr:: kable(tab_1_df, digits = 2, 
#              col.names = c('Trial Arm', 'Beta', 'SE', 'Upper CI', 'Lower CI') )
```

Figure 1 graphs the results with the means of each level alongside their confidence intervals.

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# plot results from simulated means ---------------------------------------

# Create summary stats text
df_mean_coefs_from_sim$text_label <- 0
for(i in 1: nrow(df_mean_coefs_from_sim))
df_mean_coefs_from_sim$text_label[i] <-  paste(
   "k = ", df_count_studies_not_missing $n[i],"\n", 
   round(df_mean_coefs_from_sim$mean_coefficient[i], 2),
   "[" ,
 round(df_mean_coefs_from_sim$lower_ci[i],2), 
 round(df_mean_coefs_from_sim$upper_ci[i], 2),
"]")

# recode condition for ease of plotting
df_mean_coefs_from_sim$condition <- str_replace_all(df_mean_coefs_from_sim$condition, "_", " ")

# encode colours
redish_palette <- c("medication control" = "deeppink", "medication active" = "deeppink3")
blueish_palette <- c("psychotherapy active" = "steelblue1", "psychotherapy control" = "steelblue3")

ggplot(df_mean_coefs_from_sim, aes(x = mean_coefficient, y = 1:nrow(df_mean_coefs_from_sim),
                                   colour = condition, label = text_label)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
  geom_text(vjust = +1.5, size = 4) +  # Adjust vjust and size as needed
  scale_size_continuous(guide = "none") +
  guides(colour = FALSE) + 
  scale_color_manual(values = c(redish_palette, blueish_palette)) +
  theme_minimal() +
  labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Type and Treatment Arm",
       subtitle = "metanalytically derived estimates of within group changes") +
  xlab("Standardized Mean Difference (SMD) with 95% CIs") +
  ylab("") +
  ylim(0, nrow(df_mean_coefs_from_sim) + 1) +
  xlim(-2.5, 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
  geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
  geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
  theme(axis.title.x = element_text(size = 14), 
        axis.text.x  = element_text(size = 14),
        axis.text.y = (element_blank()),
        plot.title = element_text(size = 16),
        plot.subtitle = element_text(size = 14))+
  geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
  geom_text(x = 0.2, y = 4.75, label = "Line of No Effect", color = "grey", vjust = 0.5, hjust = 0)

As can be intuited from the confidence intervals displayed, there are statistically significant differences at p<0.05 between the two control arms. Table 2 illustrates this with the output of one of the simulated models.

```{r, warning=FALSE, message = FALSE, echo=FALSE}
coefs<- 0
ses <- 0
for(i in 1: length(list_model_1_meta_reg)){

  coefs[[i]] <- coef(list_model_1_meta_reg[[i]])[[4]]  ### CAREFUL this is poor coding practice on my part
  ses[[i]] <- list_model_1_meta_reg[[i]]$se[4] ### but I can't find another way of grabbing this estimate from the
  ### rma object. It could go badly wrong if the relevelling isn't done consistently...CHECK MANUALLY
  coefficients_from_contrasts_medcontrol_psy_control <- data.frame(Beta = mean(coefs), SE = mean(ses))
}

coefficients_from_contrasts_medcontrol_psy_control$lower_ci <- coefficients_from_contrasts_medcontrol_psy_control$Beta - 1.96*coefficients_from_contrasts_medcontrol_psy_control$SE

coefficients_from_contrasts_medcontrol_psy_control$upper_ci <- coefficients_from_contrasts_medcontrol_psy_control$Beta + 1.96*coefficients_from_contrasts_medcontrol_psy_control$SE

```{r, warning=FALSE, message = FALSE, echo=FALSE}

knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control, col.names = c("Beta", "SE", "Lower CI", "Upper CI"), digits = 2)
```
